---
title: "README"
author: "Jordan S Read"
date: "`r format(Sys.time(), '%d %B, %Y')`"
output:
  md_document:
    variant: markdown_github
---

##Installation
Currently only available via github. Easiest way to install is to use the `devtools` package:

```{r echo=TRUE, eval=FALSE}
devtools::install_github("USGS-R/sensorQC")
```

This package is still very much in development, so the API may change at any time.

[![Build status](https://ci.appveyor.com/api/projects/status/pho8872wbnvaw5nt)](https://ci.appveyor.com/project/jread-usgs/sensorqc)  

[![Build Status](https://travis-ci.org/USGS-R/sensorQC.svg?branch=master)](https://travis-ci.org/USGS-R/sensorQC)  

[![Coverage Status](https://img.shields.io/coveralls/USGS-R/sensorQC.svg)](https://coveralls.io/r/USGS-R/sensorQC)

High-frequency aquatic sensor QAQC procedures. `sensorQC` imports data, and runs various statistical outlier detection techniques as specified by the user. 


###`sensorQC` Functions (as of v0.2.0)
| Function       | Title           |
| ------------- |:-------------|
| `read` | read in a file for sensor data or a config (.yml) file |
| `window`  | window sensor data for processing in chunks |
| `flag` | create data flags for a sensor |

### example usage

```{r}
library(sensorQC)
file <- system.file('extdata', 'test_data.txt', package = 'sensorQC') 
sensor <- read(file, format="wide_burst", date.format="%m/%d/%Y %H:%M")
flag(sensor, 'x == 999999', 'n > 3', 'is.na(x)')
```

Add windowing to the data to use `MAD` (median absolute deviation) test
```{r}
sensor = window(sensor, 'auto')
flag(sensor, 'x == 999999', 'n > 3', 'MAD(x) > 3')
```
