---
title: "README"
author: "Jordan S Read"
date: "`r format(Sys.time(), '%d %B, %Y')`"
output:
  md_document:
    variant: markdown_github
---

##Installation

To install the stable version of `sensorQC` package with dependencies:
```{r echo=TRUE, eval=FALSE}
install.packages("sensorQC", 
    repos = c("http://owi.usgs.gov/R","http://cran.rstudio.com/"),
    dependencies = TRUE)
```

Or to install the current development version of the package (using the `devtools` package):
```{r echo=TRUE, eval=FALSE}
devtools::install_github("USGS-R/sensorQC")
```

This package is still very much in development, so the API may change at any time.
| Name       | Status           |  
| :------------ |:-------------|  
| Linux Build: | [![Build Status](https://travis-ci.org/USGS-R/sensorQC.svg?branch=master)](https://travis-ci.org/USGS-R/sensorQC) |  
| Windows Build: | [![Build status](https://ci.appveyor.com/api/projects/status/pho8872wbnvaw5nt)](https://ci.appveyor.com/project/jread-usgs/sensorqc)  |  
| Package Tests: | [![Coverage Status](https://coveralls.io/repos/USGS-R/sensorQC/badge.svg?branch=master&service=github)](https://coveralls.io/github/USGS-R/sensorQC?branch=master) |  


High-frequency aquatic sensor QAQC procedures. `sensorQC` imports data, and runs various statistical outlier detection techniques as specified by the user. 


###`sensorQC` Functions (as of v`r packageVersion('sensorQC')`)
| Function       | Title           |
| ------------- |:-------------|
| `read` | read in a file for sensor data or a config (.yml) file |
| `window`  | window sensor data for processing in chunks |
| `flag` | create data flags for a sensor |

### example usage

```{r}
library(sensorQC)
file <- system.file('extdata', 'test_data.txt', package = 'sensorQC') 
sensor <- read(file, format="wide_burst", date.format="%m/%d/%Y %H:%M")
flag(sensor, 'x == 999999', 'persist(x) > 3', 'is.na(x)')
```

Use the `MAD` (median absolute deviation) test, and add `w` to the function call to specify "windows" (note, sensor must be windowed w/ `window()` prior to using `w`)
```{r}
sensor = window(sensor, type='auto')
flag(sensor, 'x == 999999', 'persist(x) > 3', 'MAD(x,w) > 3', 'MAD(x) > 3')
```
